\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2011-10-03 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
Added cache capabilities to pSet, readMzXMLData deprecated
 o added .cache slot to pSet class <2011-10-03 Mon>
 o added pSet initialize method to set .cache and 
   .cache$level as '0'. <2011-10-03 Mon>
 o Check that level is defined in .cache and env is locked 
   in pSet validity method. <2011-10-03 Mon>
 o updated itraqdata.RData  <2011-10-03 Mon>
 o Deprecated readMzXMLData, added defunct.Rd <2011-10-03 Mon>
 o changed readMzXMLData to readMSData in man <2011-10-03 Mon>
 o updated show MSnExp for speed <2011-10-03 Mon>
 o updated read*Data is support cache = [0|1]. <2011-10-03 Mon>
 o upda

<<readdata, echo=TRUE, cache=FALSE>>=
file <- dir(system.file(package="MSnbase",dir="extdata"),
            full.name=TRUE,
            pattern="mzXML$")
rawdata <- readMSData(file, msLevel=2, verbose=FALSE)
@

>>>>

<<readdata, echo=TRUE, cache=FALSE>>=
file <- dir(system.file(package="MSnbase", dir="extdata"),
            full.names=TRUE, pattern="mzXML$")
rawdata <- readMSData(file, msLevel=2, verbose=FALSE)
@
